Analysis paper

### 2021-06-15 analysis/analysis.Rmd
update plots

for (horizon in 1:4) {
  # plot for cases
  truth_vs_forecast_cases <- df[grepl(horizon, target)] %>%
    dplyr::filter(target_type == "case") %>%
    truth_and_pred_plot() + 
    scale_color_manual(values = colcases) + 
    labs(y = "Cases", x = "")

@@

  # plot for deaths
  truth_vs_forecast_deaths <- df[grepl(horizon, target)] %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_pred_plot()  + 
  scale_color_manual(values = coldeaths) + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "Deaths", x = "")

  filename <- here("analysis", "plots", 
                   paste0("truth-and-", horizon, "-wk-ahead_deaths"))
  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_deaths)

@@

  scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
    scores_over_time_plot(y = "interval_score") + 
    scale_color_brewer(palette = "Accent") + 
    annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
             xmax = max(forecast_dates$death_not_scored) + 14,
             ymin = 0,
             ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "WIS rel. to baseline", x = "Date")

>>>>

for (i in 1:4) {
  # plot for cases
  truth_vs_forecast_cases <- df[grepl(i, target)] %>%
    dplyr::filter(target_type == "case") %>%
    truth_and_pred_plot() + 
    scale_color_manual(values = colcases) + 
    labs(y = "Cases", x = "")

@@

  # plot for deaths
  truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_pred_plot()  + 
  scale_color_manual(values = coldeaths) + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "Deaths", x = "")

  filename <- here("analysis", "plots", 
                   paste0("truth-and-", i, "-wk-ahead_deaths"))
  ggsave(paste0(filename, ".png"), plot = truth_vs_forecast_deaths)

@@

  scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
    scores_over_time_plot(y = "interval_score") + 
    scale_color_manual(values = colcases) + 
    annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
             xmax = max(forecast_dates$death_not_scored) + 14,
             ymin = 0,
             ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "WIS rel. to baseline", x = "Date")
